LAGOS lake depth

### 2021-08-04 figures/01_contrasts.Rmd
correct old lagosus depth load command

# load LAGOSUS DEPTH
lg_raw <- lagosus_load("depth")$depth$depth
lg <- lg_raw %>%
  mutate(lagos_effort =
    forcats::fct_collapse(lg_raw$lagos_effort,
      bathymetry = "bathymetry",
      other = c("LAGOSNE", "manual", "NLA")))

>>>>

# load LAGOSUS DEPTH
lg_raw <- lagosus_load("depth")$depth$lake_depth
lg <- lg_raw %>%
  mutate(lagos_effort =
    forcats::fct_collapse(lg_raw$lagos_effort,
      bathymetry = "bathymetry",
      other = c("LAGOSNE", "manual", "NLA")))
